\section{Introduction}

The software diversity in order to manage reference is already 
great but no software give a complete satisfaction. Scientific and
educationnal content are spread in the Internet and there is currently
no way to gather them into a single and simple distributed network of repository.

This paper aims to draw what should be a good solution in order to 
spread educationnal content and scientific article in a completly distributed 
way.


\section{State of art \& Related works}

\begin{itemize}

\item \textit{P2P is a mature and production ready technology}

\item \textit{PDF indexing and searching techniques are mature and quickly growing}

\item \textit{Need to have a coherent and accurate interface for science article}

\end{itemize}

\begin{itemize}

\item \textit{Google Scholar is good but it doesn't provide an API and work as a black box}

\item \textit{Not everyone use a MacOSX but everyone should have a good user interface experience}

\item \textit{Web based solution are better for interoperability.}

\item \textit{Education should be easily accessed all over the world}

\item \textit{Some initiatives already exists but not a single open network is massively used}

\end{itemize}

\section{Problem statment}

\begin{itemize}
\item \textit{Distributed way to spread education contents like scientific article, education manual, \ldots}
\item \textit{P2P network with no central authority. Everyone should be able to find quickly accurate science article for free}
\end{itemize}

\section{Usage}

\textit{Some initiatives already exists}

\begin{itemize}
\item OverCite
\item Open Archive initiative
\item arXiv.org
\end{itemize}

\section{Contributions}

\subsection{Indexation}

\subsubsection{Bib\TeX{} analysis and reference}

\textit{Indexing, indexing, indexing\ldots}

\subsubsection{No double utility}

\textit{Avoid to have several time the same article will
be easy with an hash mechanism}

\subsection{Repository}

\subsubsection{A web interface to browse content}

\textit{A stable web interface is required in order to
deploy quickly good web interface in order to make the system
appealing.}

\subsubsection{Security issues}

\textit{In this part we will see how we can make connections
between peers safer by an authentification process. With this
system only validated papers can be broadcasted on the network.}

\subsection{Application}

\subsubsection{Different ranking methods}

\textit{Reference and ``must read papers'' against fresh new papers}

\subsubsection{Accounts made light}

\textit{Only hashes and file pointers are needed in order to make an
account to memorize the preferences. We can have a account management
website with very few ressources.}

\subsubsection{RSS utilities}

\textit{Scientists should have all the information that matters directly into
one feed.}

\subsubsection{Graphical interface to manage the current personnal repository}

\textit{The complete personnal repository is manageable by using a command line
tool or by using a graphical interface}

\subsubsection{Meta information about files}

\textit{Index files wherever et whatever they are. Indexing sections, subsections,
keywords. Indexing everything that matters.}

\subsubsection{Files distance}

\textit{In order to suggest articles that might be interesting we can use
some keywords parsing in order to see what are the contents that may be more
relevant to an user}

\section{Results}

\textit{Some statistics about arXiv and what it would require to make arxiv in
all the miror in a P2P distributed network}

\section{Conclusion}

\textit{Additionnal time and administrative power is required in order to
make this project come true}

