\section{Survey on distributed delivery system}

% What is the problem
% What are the contributions
% What are the conclusions
% What is the support for the conclusions

This paper will attempt to describe what are the most influencial papers in order to
understand the Overcite article
\cite{overcite}. I looked through all the articles listed in the references to decide whether 
or not this paper was related to it. The reference list was 49 articles long. I used the 
number of citations in the article to decide if it was well known enough.
According to Google Scholar, the articles cited in this paper are all cited over several 
hundreds time in other papers. This way of grading the articles is appropriate 
for finding a seminal paper but 
it's not a very efficient paper to evaluate the new and not yet well referenced papers.
Hence, it's possible that more recent and accurate papers influenced Overcite but are 
currently not known enough.

\subsection{Bit Torrent, a major P2P system}

One of the most influencial papers dealing with P2P technologies is the one written by Bram 
Cohen, creator of the Bit Torrent protocol. This paper gives all the basis of the Bit Torrent protocol :
the Tit-For-Tat, the Pareto Efficient Goal, and the Tracker Concept. All these concepts that seem natural
right now in the P2P world were introduced in this paper \cite{Cohen03incentivesbuild}.
We can see that there is no mention of the DHT in this paper. It would be interesting
to see how the Bit Torrent protocol could get rid of the tracker using DHT systems.
However, this article remains a very important paper in the history of P2P systems.

\subsection{Searching on P2P networks}

To build a really efficient P2P scientific articles network we need to also
provide a very efficient and scalable way of searching information through out this network.

Several way have been proposed to do this \cite{Yang02improvingsearch}. These methods give
very good results if we take the searching technique BFS as a baseline. But the status of implementation
of these techniques into current P2P systems is still unknown. It could be interesting to see how much
the ideas of this article could be applied into a real production system.

A different way of providing information about the peers has been released.
One of the most known is
the DHT (Distributed Hash Table). An implementation have been provided
by Sean Rhea \cite{Rhea:2005:OPD:1090191.1080102}.
This implementation (OpenDHT) deprecated in 2006. According to the 
\href{http://opendht.org}{website's project}, this is mostly due to
more mature services, such as Amazon Dynamo and Cassandra,
being massively used by well known web actors . DHT implementation seems 
to be mature enough to support such large
services like Facebook or Amazon. So this paper contributed
 to the diffusion of the DHT concepts to a wider public.
Powered during his work by planet lab to test it, Sean Rhea added 
his work to build a good implementation \href{bamboo-dht.org}{Bamboo}.

Other techniques are also used to improve the quality of search power in P2P network. We can quote
\cite{Reynolds_efficientpeer-to-peer} in order to see that bloom filters, cache, and incremental
results also enhance the quality and speed of the results. A very interesting study would be to
see how these techniques are integrated inside recent P2P technologies among clusters like Cassandra
or other system. There is not a single and united developement of P2P techniques so the advance of 
each project is very heterogeneous. Providing compatiable and very stable librairies to all these projects would
be a sign of coherent development among the P2P developers community.

\subsection{Extract and indexing papers}

Browsing papers is not enough, making connections between them is really important to make the really 
important papers come out of the whole set. A current and quite relevant way to
index content is the Google Page Rank system. But citations are not only relevant to the 
topic of an article. Quoting very known articles helps to consider the paper as more mature
and the author seems to be more aware of all the important work\cite{Lawrence99digitallibraries}. The Overcite project
is really 
active and well referenced. Even Google Scholar uses it as a first choice provider in most cases
for referencing scientific papers.

\pagebreak
